
% Bibliography references for webography chapter
\begin{thebibliography}{99}

    \bibitem{uml_importance}
    Object Management Group. (2017). \textit{Unified Modeling Language Specification}. Retrieved from https://www.omg.org/spec/UML/
    
    \bibitem{ai_diagramming}
    Chen, P., \& Wang, L. (2023). Artificial Intelligence in Software Design Automation. \textit{IEEE Software Engineering Journal}, 45(3), 78-92.
    
    \bibitem{gui_limitations}
    Smith, J. A. (2022). Challenges in Traditional Diagramming Tools: A Productivity Analysis. \textit{Software Development Quarterly}, 18(2), 156-171.
    
    \bibitem{plantuml_guide}
    PlantUML Team. (2024). \textit{PlantUML Language Reference Guide}. Retrieved from https://plantuml.com/guide
    
    \bibitem{workflow_integration}
    Anderson, M., \& Brown, K. (2023). Integration Challenges in Modern Development Workflows. \textit{DevOps Today}, 12(4), 34-48.
    
    \bibitem{diagramming_ai}
    Diagramming AI Platform. (2024). \textit{AI-Powered Diagram Generation}. Retrieved from https://diagramming-ai.com/
    
    \bibitem{chatuml}
    ChatUML Development Team. (2024). \textit{Conversational UML Generation Platform}. Retrieved from https://chatuml.com/
    
    \bibitem{existing_tools_analysis}
    Rodriguez, C., et al. (2023). Comparative Analysis of Automated Diagramming Tools. \textit{Software Tools Review}, 29(7), 112-127.
    
    \bibitem{nlp_diagramming}
    Kim, S., \& Lee, H. (2023). Natural Language Processing for Automated Software Modeling. \textit{AI in Software Engineering}, 8(1), 23-39.
    
    \bibitem{plantuml_standards}
    ISO/IEC 19505. (2012). \textit{Information technology - Object Management Group Unified Modeling Language}. International Organization for Standardization.
    
    \bibitem{microservices_design}
    Newman, S. (2021). \textit{Building Microservices: Designing Fine-Grained Systems}. O'Reilly Media.
    
    \bibitem{plantuml_documentation}
    PlantUML. (2024). \textit{Official Documentation and User Guide}. Retrieved from https://plantuml.com/
    
    \bibitem{plantuml_formats}
    PlantUML. (2024). \textit{Output Formats and Integration Guide}. Retrieved from https://plantuml.com/output-formats
    
    \bibitem{plantuml_enterprise}
    Roques, A. (2023). PlantUML in Enterprise Environments: Scalability and Performance. \textit{Enterprise Software Journal}, 15(6), 89-103.
    
    \bibitem{agile_manifesto}
    Beck, K., et al. (2001). \textit{Manifesto for Agile Software Development}. Retrieved from https://agilemanifesto.org/
    
    \bibitem{agile_benefits}
    Dingsøyr, T., \& Moe, N. B. (2014). Towards Principles of Large-Scale Agile Development. \textit{Agile Software Development}, 1-8.
    
    \bibitem{scrum_advantages}
    Schwaber, K., \& Sutherland, J. (2020). \textit{The Scrum Guide}. Retrieved from https://scrumguides.org/
    
    \bibitem{scrum_guide}
    Schwaber, K., \& Sutherland, J. (2020). The Definitive Guide to Scrum: The Rules of the Game. \textit{Scrum.org}.
    
    \bibitem{empirical_scrum}
    Sutherland, J. (2014). \textit{Scrum: The Art of Doing Twice the Work in Half the Time}. Crown Business.
    
    \bibitem{scrum_roles}
    Pichler, R. (2010). \textit{Agile Product Management with Scrum: Creating Products that Customers Love}. Addison-Wesley.
    
    \bibitem{scrum_events}
    Cohn, M. (2009). \textit{Succeeding with Agile: Software Development Using Scrum}. Addison-Wesley.
    
    \bibitem{scrum_artifacts}
    Rubin, K. S. (2012). \textit{Essential Scrum: A Practical Guide to the Most Popular Agile Process}. Addison-Wesley.
    
    \bibitem{modeling_languages}
    Fowler, M. (2003). \textit{UML Distilled: A Brief Guide to the Standard Object Modeling Language}. Addison-Wesley.
    
    \bibitem{uml_comparison}
    Holt, J., Perry, S., \& Brownsword, M. (2012). Model-Based Requirements Engineering. Institution of Engineering and Technology.
    
    \bibitem{uml_specification}
    Object Management Group. (2017). \textit{OMG Unified Modeling Language (OMG UML) Version 2.5.1}. Retrieved from https://www.omg.org/spec/UML/2.5.1/
    
    \bibitem{uml25_diagrams}
    Pilone, D., \& Pitman, N. (2005). \textit{UML 2.0 in a Nutshell}. O'Reilly Media.
    
    \end{thebibliography}